Title

### 2013-02-09 inc/model_results/shapes/shapes.tex
added short titles for the remaining figures
continue discussion on shape/density

\subsection{Trends for Initial Shapes}

@@

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:compare_shape_N1}
    \input{shapes_N1}
  }
  \\
  \subfloat[][]{
    \label{fig:compare_shape_N1e6}
    \input{shapes_N1e6}
  }
  \caption{
    Transverse (solid) and longitudinal (dashed) dynamics of three example pulses for three length/width ratios ($\xi$). 
    The red lines represent a prolate pulse (a ``pancake'') with $\xi=1/3$, green lines for a spherical pulse with $\xi=1$, and blue for oblate (a ``cigar'') having $\xi=3$.
  }
  \label{fig:compare_shape}
\end{figure}

@@

>>>>

\subsection{Trends for Initial Shapes} \label{sec:initial_shapes}

@@

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:compare_shape_N1}
    \input{shapes_N1}
  }
  \\
  \subfloat[][]{
    \label{fig:compare_shape_N1e6}
    \input{shapes_N1e6}
  }
  \caption[AG simulation of free-space pulse expansion]{
    Transverse (solid) and longitudinal (dashed) dynamics of three example pulses for three length/width ratios ($\xi$). 
    The red lines represent a prolate pulse (a ``pancake'') with $\xi=1/3$, green lines for a spherical pulse with $\xi=1$, and blue for oblate (a ``cigar'') having $\xi=3$.
  }
  \label{fig:compare_shape}
\end{figure}

@@

I have shown that a prolate spheroid pulse shape is preferred for UEM, both for generation in SECTION %TODO link to Child law discussion
and in this section for propagation.
Further I have shown in %TODO link to section where I show that initial conditions create shorter pulses than laser
that electron pulses shorter than the laser pulse duration are likely occurances.
Henceforth I shall only consider prolate pulses when a choice of initial pulse shape is possible.

### 2013-02-09 inc/model_results/spacecharge/spacecharge.tex
continue discussion on shape/density

>>>>

A full analysis of how high the charge density may be before deleterious space-charge become unmanagable would be a sizable task.
Much discussion could be had on the degree of distortion allowable as well as considerations of the initial shape of the pulse and length and arrangement of the column and its constituent elements.

Purely for illustrative purposes I am including \ref{fig:spacecharge} to provide an intuition about the order of magnitude of these effects.

\begin{figure}
  \centering
  \begin{tikzpicture}
    \input{spacecharge_data}
  \end{tikzpicture}
  \caption[Free-space pulse evolution vs charge density]{
    The final HW1/eM width (solid) and length (dashed) of similar initial size pulses for different number of electrons in the pulse.
    The pulse is generated by 1 mm (HW1/eM) width 1 ps laser pulses with 0.5eV excess photoemission energy. The pulse then traverses a 20mm acceleration region and a 15cm drift region.
  }
  \label{fig:spacecharge}
\end{figure}
